---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(tidyverse)
```

# ctppflows

<!-- badges: start -->
<!-- badges: end -->

The goal of ctppflows is to provide tract level home-work flow data from the 
Census Transportation Planning Package (CTPP) in a much more convenient format
for R users, particularly those without a Microsoft Access license.

The entire tract dataset is included in the package as a documented R object,
and the package also contains helper functions for properly calculating aggregate
flows and their margins of error.

## Installation

You can install the development version of ctpp_flows from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("gregmacfarlane/ctpp_flows")
```
## Example

After installing the library, the `ctpp_flows` dataset is available as a tibble
lazy-loaded into your environment.

```{r example}
library(ctppflows)

# load 
ctpp_flows
```

The `aggregate_flows` function will aggregate the flows to a state or county.
The aggregated margin of error is computed as

$$ \sqrt{\sum_{i=1}^N MOE_i^2}$$

The results can then be passed into other R formatting functions. 

```{r pressure}
aggregate_flows("state") %>%
  filter(residence == "49") %>% #utah residents
  filter(flow > 1000)
```

