---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(tidyverse)
```

# ctppflows

<!-- badges: start -->
<!-- badges: end -->

The goal of ctppflows is to provide tract level home-work flow data from the 
Census Transportation Planning Package (CTPP) in a much more convenient format
for R users, particularly those without a Microsoft Access license.

The entire tract dataset is included in the package as a documented R object,
and the package also contains helper functions for properly calculating aggregate
flows and their margins of error.

## Installation

You can install the development version of ctpp_flows from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("gregmacfarlane/ctpp_flows")
```
## Example

After installing the library, the `ctpp_flows` dataset is available as a tibble
lazy-loaded into your environment.

```{r example}
library(ctppflows)

# load 
ctpp_flows
```

The `aggregate_flows` function will aggregate the flows to a state or county.
The aggregated margin of error is computed as

$$ \sqrt{\sum_{i=1}^N MOE_i^2}$$
```{r aggregate}
aggregate_flows("state")
```

The results can then be passed into other R formatting functions. For instance,
we could make a plot of where workers into Salt Lake County reside.

```{r pressure}
# get workplaces in salt lake county
sl_workers <- ctpp_flows %>%
  mutate(county = str_c(get_state(workplace), get_county(workplace))) %>%
  filter(county == "49035") %>%
  filter(flow > 50) %>%
  group_by(residence) %>%
  summarise(flow = sum(flow))

ut_tr <- tigris::tracts("Utah", class = "sf", progress_bar = FALSE) %>%
  select(GEOID) %>%
  left_join(sl_workers, by = c("GEOID" = "residence"))

ggplot(ut_tr %>% filter(flow > 0), aes(fill = log(flow))) +
  geom_sf() + scale_fill_viridis_b()
```


